Thesis outline

### 2017-06-21 KellyDouglass/Thesis/Tables/Paper1/XMPtable.tex
Updated Paper 3
Changed table names

\begin{tabu} to 0.75\linewidth {ccccccc}
Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
\hline \\
268470 & \RA{13}{18}{17}{.82} & +\dec{02}{12}{59}{.83} & 0.0252 & 7.06 & $\pm$0.37 & Void \\
1422637 & \RA{14}{18}{12}{.14} & +\dec{13}{59}{33}{.98} & 0.0261 & 7.15 & $\pm$0.41 & Wall \\
839665 & \RA{08}{09}{53}{.53} & +\dec{29}{17}{04}{.82} & 0.0281 & 7.18 & $\pm$0.44 & Void \\
1168448 & \RA{11}{06}{41}{.00} & +\dec{45}{19}{09}{.28} & 0.0220 & 7.19 & $\pm$0.46 & Wall \\
1299291 & \RA{12}{17}{14}{.02} & +\dec{43}{18}{53}{.36} & 0.0233 & 7.21 & $\pm$0.42 & Wall \\
1170573 & \RA{11}{05}{39}{.42} & +\dec{46}{03}{28}{.37} & 0.0250 & 7.24 & $\pm$0.34 & Wall \\
2288717 & \RA{10}{46}{12}{.18} & +\dec{21}{31}{37}{.37} & 0.0248 & 7.27 & $\pm$0.48 & Wall \\
955643 & \RA{11}{42}{03}{.02} & +\dec{49}{21}{25}{.18} & 0.0244 & 7.28 & $\pm$0.44 & Wall \\
1344311 & \RA{12}{33}{13}{.64} & +\dec{11}{10}{28}{.46} & 0.0245 & 7.29 & $\pm$0.50 & Wall \\
1254352 & \RA{13}{29}{02}{.45} & +\dec{10}{54}{55}{.80} & 0.0237 & 7.30 & $\pm$0.44 & Wall \\
1857820 & \RA{08}{45}{00}{.34} & +\dec{27}{16}{47}{.04} & 0.0257 & 7.31 & $\pm$0.48 & Wall \\
866876 & \RA{09}{04}{57}{.96} & +\dec{41}{29}{36}{.42} & 0.0240 & 7.32 & $\pm$0.40 & Wall \\
833588 & \RA{08}{43}{10}{.71} & +\dec{43}{08}{53}{.58} & 0.0245 & 7.34 & $\pm$0.41 & Wall \\
283263 & \RA{14}{14}{12}{.88} & +\dec{01}{50}{12}{.88} & 0.0255 & 7.35 & $\pm$0.43 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & 7.36 & $\pm$0.43 & Wall \\
1389829 & \RA{14}{31}{01}{.38} & +\dec{38}{04}{21}{.50} & 0.0269 & 7.41 & $\pm$0.46 & Wall \\
858951 & \RA{09}{31}{39}{.60} & +\dec{49}{49}{56}{.85} & 0.0251 & 7.46 & $\pm$0.46 & Wall \\
1270221 & \RA{13}{27}{39}{.85} & +\dec{50}{54}{09}{.69} & 0.0295 & 7.49 & $\pm$0.43 & Wall \\
431383 & \RA{08}{58}{44}{.96} & +\dec{50}{29}{58}{.98} & 0.0230 & 7.52 & $\pm$0.60 & Void \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & 7.55 & $\pm$0.35 & Void \\
1322765 & \RA{14}{15}{05}{.58} & +\dec{36}{22}{57}{.77} & 0.0273 & 7.57 & $\pm$0.40 & Wall\\
\end{tabu}

\caption[Extreme low-metallicity dwarf galaxies]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.  Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.  Further study of these galaxies is recommended to confirm metallicity values and identify any shared characteristics.}

>>>>

\begin{tabular}{ccccccc}
Index\footnote{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
\hline \\
268470 & \RA{13}{18}{17}{.82} & +\dec{02}{12}{59}{.83} & 0.0252 & 7.06 & $\pm$0.37 & Void \\
1422637 & \RA{14}{18}{12}{.14} & +\dec{13}{59}{33}{.98} & 0.0261 & 7.15 & $\pm$0.41 & Wall \\
839665 & \RA{08}{09}{53}{.53} & +\dec{29}{17}{04}{.82} & 0.0281 & 7.18 & $\pm$0.44 & Void \\
1168448 & \RA{11}{06}{41}{.00} & +\dec{45}{19}{09}{.28} & 0.0220 & 7.19 & $\pm$0.46 & Wall \\
1299291 & \RA{12}{17}{14}{.02} & +\dec{43}{18}{53}{.36} & 0.0233 & 7.21 & $\pm$0.42 & Wall \\
1170573 & \RA{11}{05}{39}{.42} & +\dec{46}{03}{28}{.37} & 0.0250 & 7.24 & $\pm$0.34 & Wall \\
2288717 & \RA{10}{46}{12}{.18} & +\dec{21}{31}{37}{.37} & 0.0248 & 7.27 & $\pm$0.48 & Wall \\
955643 & \RA{11}{42}{03}{.02} & +\dec{49}{21}{25}{.18} & 0.0244 & 7.28 & $\pm$0.44 & Wall \\
1344311 & \RA{12}{33}{13}{.64} & +\dec{11}{10}{28}{.46} & 0.0245 & 7.29 & $\pm$0.50 & Wall \\
1254352 & \RA{13}{29}{02}{.45} & +\dec{10}{54}{55}{.80} & 0.0237 & 7.30 & $\pm$0.44 & Wall \\
1857820 & \RA{08}{45}{00}{.34} & +\dec{27}{16}{47}{.04} & 0.0257 & 7.31 & $\pm$0.48 & Wall \\
866876 & \RA{09}{04}{57}{.96} & +\dec{41}{29}{36}{.42} & 0.0240 & 7.32 & $\pm$0.40 & Wall \\
833588 & \RA{08}{43}{10}{.71} & +\dec{43}{08}{53}{.58} & 0.0245 & 7.34 & $\pm$0.41 & Wall \\
283263 & \RA{14}{14}{12}{.88} & +\dec{01}{50}{12}{.88} & 0.0255 & 7.35 & $\pm$0.43 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & 7.36 & $\pm$0.43 & Wall \\
1389829 & \RA{14}{31}{01}{.38} & +\dec{38}{04}{21}{.50} & 0.0269 & 7.41 & $\pm$0.46 & Wall \\
858951 & \RA{09}{31}{39}{.60} & +\dec{49}{49}{56}{.85} & 0.0251 & 7.46 & $\pm$0.46 & Wall \\
1270221 & \RA{13}{27}{39}{.85} & +\dec{50}{54}{09}{.69} & 0.0295 & 7.49 & $\pm$0.43 & Wall \\
431383 & \RA{08}{58}{44}{.96} & +\dec{50}{29}{58}{.98} & 0.0230 & 7.52 & $\pm$0.60 & Void \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & 7.55 & $\pm$0.35 & Void \\
1322765 & \RA{14}{15}{05}{.58} & +\dec{36}{22}{57}{.77} & 0.0273 & 7.57 & $\pm$0.40 & Wall\\
\end{tabular}

\caption[Extremely low-metallicity dwarf galaxies in 135 galaxy sample]{Details of the 21 extreme low gas-phase metallicity ($12 + \log(\text{O}/\text{H}) < 7.6$) galaxies found.  Four of these galaxies are located in voids (about 10\% of the void dwarf population measured) and seventeen are in more dense regions (about 19\% of the wall dwarf population measured); thus, there does not seem to be a special population of extreme low-metallicity galaxies in voids.  Further study of these galaxies is recommended to confirm metallicity values and identify any shared characteristics.}

### 2017-06-21 KellyDouglass/Thesis/Tables/Paper1/results_table_short.tex
Updated Paper 3
Changed table names

\begin{tabu} to 0.75\linewidth {cccccccc}
Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
\hline \\
63713 & \RA{09}{20}{04}{.27} & -\dec{00}{30}{08}{.97} & 0.0257 & -16.73 & 7.80 & $\pm$0.41 & Wall \\
73537 & \RA{09}{25}{24}{.23} & +\dec{00}{12}{40}{.39} & 0.0250 & -16.94 & 7.94 & $\pm$0.34 & Wall \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & -16.81 & 7.55 & $\pm$0.35 & Void \\
168874 & \RA{11}{45}{13}{.16} & -\dec{01}{48}{17}{.68} & 0.0273 & -16.99 & 8.16 & $\pm$0.31 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & Wall\\
\end{tabu}

\caption[Dwarf galaxy properties]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Metallicity values are calculated using the direct $T_e$ method, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS survey to identify whether or not it is inside a void, it is labeled as Uncertain.  Table \ref{tab:Results_P1} is published in its entirety online in a machine-readable format.  A portion is shown here for guidance regarding its form and content.}

>>>>

\begin{tabular}{cccccccc}
Index\footnote{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & Void/Wall \\
\hline \\
63713 & \RA{09}{20}{04}{.27} & -\dec{00}{30}{08}{.97} & 0.0257 & -16.73 & 7.80 & $\pm$0.41 & Wall \\
73537 & \RA{09}{25}{24}{.23} & +\dec{00}{12}{40}{.39} & 0.0250 & -16.94 & 7.94 & $\pm$0.34 & Wall \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & -16.81 & 7.55 & $\pm$0.35 & Void \\
168874 & \RA{11}{45}{13}{.16} & -\dec{01}{48}{17}{.68} & 0.0273 & -16.99 & 8.16 & $\pm$0.31 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & Wall\\
\end{tabular}

\caption[Properties of subseet of 135 dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Metallicity values are calculated using the direct $T_e$ method, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS survey to identify whether or not it is inside a void, it is labeled as Uncertain.  Table \ref{tab:Results_P1} is published in its entirety online in a machine-readable format.  A portion is shown here for guidance regarding its form and content.}

### 2017-06-21 KellyDouglass/Thesis/Tables/Paper2/results_table_short.tex
Updated Paper 3
Changed table names

\begin{tabu} to \textwidth {cccccccccccc}
Index\footnote[1]{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{N}}{\text{H}} \right)$} & \multicolumn{2}{c}{$\log \left( \frac{\text{N}}{\text{O}} \right)$} & Void/Wall \\
\hline \\
63713 & \RA{09}{20}{04}{.27} & -\dec{00}{30}{08}{.97} & 0.0257 & -16.73 & 7.80 & $\pm$0.41 & 6.83 & $\pm$0.28 & -0.97 & $\pm$0.49 & Wall \\
73537 & \RA{09}{25}{24}{.23} & +\dec{00}{12}{40}{.39} & 0.0250 & -16.94 & 7.94 & $\pm$0.34 & 6.76 & $\pm$0.24 & -1.18 & $\pm$0.41 & Wall \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & -16.81 & 7.55 & $\pm$0.35 & 6.73 & $\pm$0.24 & -0.82 & $\pm$0.42 & Void \\
168874 & \RA{11}{45}{13}{.16} & -\dec{01}{48}{17}{.68} & 0.0273 & -16.99 & 8.16 & $\pm$0.31 & 6.94 & $\pm$0.21 & -1.21 & $\pm$0.37 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & 6.71 & $\pm$0.31 & -0.65 & $\pm$0.53 & Wall\\
\end{tabu}

\caption[Analyzed dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Metallicity values are calculated using the direct $T_e$ method, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS to identify whether or not it is inside a void, it is labeled as Uncertain.  (This table is available in its entirety in machine-readable form.)}

>>>>

\begin{tabular}{cccccccccccc}
Index\footnote{KIAS-VAGC galaxy index number} & R.A. & Decl. & Redshift & $M_r$ & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{O}}{\text{H}} \right)$} & \multicolumn{2}{c}{$12 + \log \left( \frac{\text{N}}{\text{H}} \right)$} & \multicolumn{2}{c}{$\log \left( \frac{\text{N}}{\text{O}} \right)$} & Void/Wall \\
\hline \\
63713 & \RA{09}{20}{04}{.27} & -\dec{00}{30}{08}{.97} & 0.0257 & -16.73 & 7.80 & $\pm$0.41 & 6.83 & $\pm$0.28 & -0.97 & $\pm$0.49 & Wall \\
73537 & \RA{09}{25}{24}{.23} & +\dec{00}{12}{40}{.39} & 0.0250 & -16.94 & 7.94 & $\pm$0.34 & 6.76 & $\pm$0.24 & -1.18 & $\pm$0.41 & Wall \\
75442 & \RA{13}{13}{24}{.25} & +\dec{00}{15}{02}{.95} & 0.0264 & -16.81 & 7.55 & $\pm$0.35 & 6.73 & $\pm$0.24 & -0.82 & $\pm$0.42 & Void \\
168874 & \RA{11}{45}{13}{.16} & -\dec{01}{48}{17}{.68} & 0.0273 & -16.99 & 8.16 & $\pm$0.31 & 6.94 & $\pm$0.21 & -1.21 & $\pm$0.37 & Wall \\
184308 & \RA{09}{39}{09}{.38} & +\dec{00}{59}{04}{.15} & 0.0244 & -16.73 & 7.36 & $\pm$0.43 & 6.71 & $\pm$0.31 & -0.65 & $\pm$0.53 & Wall\\
\end{tabular}

\caption[Chemical abundances of subset of 135 dwarf galaxies]{Five of the 135 dwarf galaxies analyzed from SDSS DR7.  The flux values for all required emission lines can be found in the MPA-JHU value-added catalog.  Metallicity values are calculated using the direct $T_e$ method, with error estimates via a Monte Carlo method.  The void catalog of \cite{Pan12} is used to classify the galaxies as either Void or Wall.  If a galaxy is located too close to the boundary of the SDSS to identify whether or not it is inside a void, it is labeled as Uncertain.  (This table is available in its entirety in machine-readable form.)}

### 2017-06-21 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Changed table names

    \caption[Abundance statistics]{Statistics of the gas-phase oxygen, nitrogen, 
    and nitrogen relative to oxygen abundances in void and wall galaxies in each 
    of the absolute magnitude ranges listed.  Most of these results are not 
    statistically significant, as shown in Figs. 
    \ref{fig:met1sig}--\ref{fig:NO_bright}.  However, the shifts in chemical 
    abundances between the two environments are predominately in the same 
    direction for each of the magnitude bins, suggesting that there is some 
    influence on the chemical evolution of galaxies by the large-scale 
    environment.   Void galaxies have slightly higher oxygen and nitrogen 
    abundances than wall galaxies, but void galaxies have slightly lower N/O 
    ratios than wall galaxies.}

>>>>

    \caption[Abundance statistics of 135 dwarf galaxy sample]{Statistics of the 
    gas-phase oxygen, nitrogen, and nitrogen relative to oxygen abundances in 
    void and wall galaxies in each of the absolute magnitude ranges listed.  
    Most of these results are not statistically significant, as shown in Figs. 
    \ref{fig:met1sig}--\ref{fig:NO_bright}.  However, the shifts in chemical 
    abundances between the two environments are predominately in the same 
    direction for each of the magnitude bins, suggesting that there is some 
    influence on the chemical evolution of galaxies by the large-scale 
    environment.   Void galaxies have slightly higher oxygen and nitrogen 
    abundances than wall galaxies, but void galaxies have slightly lower N/O 
    ratios than wall galaxies.}

### 2017-06-21 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Changed table names

    \caption[Abundance statistics]{Statistics on the gas-phase oxygen, nitrogen, 
    and nitrogen relative to oxygen abundances in dwarf void and wall galaxies.  
    Combined with the histograms in Figures 
    \ref{fig:met1sig_P3}--\ref{fig:NOratio_P3}, these results indicate an 
    influence on the chemical evolution of galaxies by the large-scale 
    environment, especially on the relative abundance of nitrogen to oxygen.  
    Void galaxies have slightly higher oxygen and nitrogen abundances than wall 
    galaxies, but void galaxies have slightly lower N/O ratios than wall 
    galaxies.}

>>>>

    \caption[Abundance statistics of full dwarf galaxy sample]{Statistics on the 
    gas-phase oxygen, nitrogen, and nitrogen relative to oxygen abundances in 
    dwarf void and wall galaxies.  Combined with the histograms in Figures 
    \ref{fig:met1sig_P3}--\ref{fig:NOratio_P3}, these results indicate an 
    influence on the chemical evolution of galaxies by the large-scale 
    environment, especially on the relative abundance of nitrogen to oxygen.  
    Void galaxies have slightly higher oxygen and nitrogen abundances than wall 
    galaxies, but void galaxies have slightly lower N/O ratios than wall 
    galaxies.}
